Discrete Ordinates

### 2017-06-03 docprep/chapimpl.tex
Deleted error
Added a section label to the vector flattening section
Updated the header
Minor fixes and added some figs

%%
%% This is file `chapall.tex',
%% generated with the docstrip utility.
%%
%% The original source files were:
%%
%% ths.dtx  (with options: `chapmin,addfig,addtbl,addbib,addglo')
%% 
%% IMPORTANT NOTICE:
%% 
%% For the copyright see the source file.
%% 
%% Any modified versions of this file must be renamed
%% with new filenames distinct from chapall.tex.
%% 
%% For distribution of the original source see the terms
%% for copying and modification in the file ths.dtx.
%% 
%% This generated file may be distributed as long as the
%% original source files, as listed above, are part of the
%% same distribution. (The sources need not necessarily be
%% in the same archive or directory.)

 %% ... sample chapter ...

@@

The code is implemented in C++ and requires a C0x11 complianct compiler. The user interface is written using the Qt5 framework. GPU computation is performed via CUDA which must be compiled seperatly by Nvidia's proprietary compiler, \texttt{nvcc}.

\section{Vector Flattening}

@@

SHOW CARBON ELEMENTAL DATA

@@

Once the data is parsed, weighted combinations of elemental data is used to create material cross sections. The details of this computation are covered in Section~\ref{sec:

>>>>

%%
%% Edward T. Norris
%% Discrete Ordinates Computed Tomography Organ Dose Simulator (DOCTORS)
%% 
%% === Implementation ===
%%

@@

The code is implemented in C++ and requires a C0x11 compliant compiler. The user interface is written using the Qt5 framework. GPU computation is performed via CUDA which must be compiled seperatly by Nvidia's proprietary compiler, \texttt{nvcc}.

\section{Vector Flattening}\label{sec:flatten}

@@

Figure~\ref{fig:sigmacomp} shows the microscopic cross section data pulled from

\begin{figure}
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/sigmacomp1}
        \caption{}
        \label{fig:ampx1}
    \end{subfigure}
    ~
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{figs/sigmacomp2}
        \caption{}
        \label{fig:ampx2}
    \end{subfigure}
    \caption{The microscopic cross section in bars for hydrogen and oxygen. Both subfigures show identical data, (a) shows the entire data range available in the reference data library and (b) shows only the data range applicable to DOCTORS.}\label{fig:sigmacomp}
\end{figure}

@@

Once the data is parsed, weighted combinations of elemental data is used to create material cross sections.

MT AND MF NUMBERS
